---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2ggplot

The goal of add2ggplot is to add more theme for your ggplot object.

## Installation

You can install the released version of add2ggplot from [Github](https://github.com/JiaxiangBU/add2ggplot) with:

```{r eval=F}
devtools::install_github('JiaxiangBU/add2ggplot')
```

```{r eval=F}
library(add2ggplot)
```


## Examples

```{r}
library(add2ggplot)
```

```{r}
plot_logo <- add_logo(
  plot_path = "man/figures/logo.png",
  logo_path = "man/figures/jiaxiang.png",
  logo_position = "bottom right",
  logo_scale = 5)
plot_logo
```


## To-dos

1. [x] Added license
1. [x] Add references for the function `theme_du_bois`
1. [ ] Added examples in the function `theme_du_bois`
1. [ ] Extract the colors from an image and build a customized palette.
1. [ ] Add badge
1. [ ] Added coc.

